\chapter{Career}
	\begin{sansserif}
		\para{Well, \textbf{the career to choose}. It may be a simple question: \textit{What do you wanna do buddy?} But the answer? absolutely not. You have to chose something that you will be doing in the rest of your life... I've talked about \textit{What} and \textit{Why} I have chosen in this chapter :D}
	\end{sansserif} \clearpage
	
	\para{Choosing what to do. If you are young (somehow under 16 or 17) you may have many options in your head, or have none, it's totally natural. You are not OLD enough and your brain doesn't care about this, but after a while, becoming an adult, your brain, will create something in your head that you say to yourself \say{I have to finally make my decision and choose something to do and to be!} Well it happened for me. When I was 17 (11th grade at high school) I thought: \say{well I don't what to be?! How about to follow and be a good example of the best of the things I see?}}
	
	\para{Our calculus teacher was the best ever I saw, well I decided to be a very nice math teacher. I talked to him and he told: \say{You are absoultly a foo, go and find something which really fits you. It will a waste for you to be tearcher!!} He was somehow right, I reallized in a while. I love teaching but it is not my type, I needed something more attractive.}
	
	\para{Once a day, a friend of mine told me: \say{Go and find yourself a good video course for programming. You will definitely love programming, I see it inside of you buddy.} Well after some searching I found \textit{Python masterclass} by \textit{Tim Buchalka} AND pandemic hit :)) I started watching this reallllllllly niiiiiiiiice course and finally found it: \say{\textbf{Programming}}, with no doubt programming will be the thing I was seeking \textsf{:D}}
	
	\para{The journey started. I was seeing nearly 5 videos per day, seriously taking notes and reading Python documentation. I was the happiest Python learner in the world. I read, nearly every part of the documentation, every \textit{type}\footnote{type: the datatypes which are built-in to Python such as \texttt{str}, \texttt{int} and \texttt{dict} types} which was tought by Tim, I read the documentation afterwards and learned way more than the course.}
	
	\para{Time passed and I got into 12th grade and abandoned learning Python due to \textit{entrance exam of university} or in short \textit{KonKoor}. I really stopped learning, after a very long year and one day after the exam, I downloaded nearly 60GB of videos just for one course: \textit{Python Deep Dive 1-4}. This is the most brilliant course ever, it really teaches you the best things and the most important things you HAVE TO know. I finished it before starting of the first semester of my university.}
	
	\para{Thanks to Allah, I was accepted as a \textit{Computer Engineering} student at \textit{Isfahan University}. I started joining Python communities created in Telegram, and after the first semester finished, I became one of the Admins of those groups \textsf{:D}}
	
	\para{Then I found someone who I really like and is one of my best friends :) \textit{Seyed Iliya}. He is really nice, and a really nice Python developer as well. We started working on real world projects and had a collaboration of something called JsonicDB\footnote{a database toolkit, written specifically for JSON datatype}}
	
	\para{At that time, WE wanted to be professional back-end engineers and started watching courses on that field, BUT: 
	\begin{itemize}
		\item for me: the 3rd semester started and it was not online (thanks Allah for that)
		\item for him: He had to study for KonKoor
	\end{itemize} So everything was nearly stopped again :/
	}

	\para{However going to university, although just for one semester, changed my way, it really changed it. After studying math, searching for the hot fields in programming and \underline{meeting new people with new expertise}, I made my one-step-to-final decision: \textit{Data Science}.}
	
	\para{Data science is sexy isn't it? It needs a deep knowledge of the both worlds, programming and science, also learning it takes time and effort. The 3rd semester passes and I more fall in love with the field.}
	
	\para{After searching and making my final decisions, I met Homayoun Sadeghi, a DevOps expert. I remembered the days I liked back-end and DevOps world and missed it :( but there were a solution for it: \textit{MLOps} field, one of the hardest fields anyone can choose and the final decision was made: \say{I want to be an MLOps specialist \textsf{:D}}}
	
	\para{I have to confess that I really like this journey AND this is a really hard field to learn and to be a good one in it. It needs many knowledge about maaaaaaaanay things, It is shaped from three worlds: Machine learning (data science) + Development (programming) + Operation (the server and all of its stuff world).}
	
	\para{After all this is what I chose and this is the things which shows my learning and career way, I may or may not change it future. I just concentrate on learning and learning and learning.}
	
	\para{Thanks}