\chapter{Courses}
		\begin{sansserif}
			Well, the major part of the summer is the courses, in this chapter I will introduce the courses I want to watch and some useful information about them.\newline
			
			\noindent Eash course is tagged with these:
			\begin{itemize}
				\item Learning curse
				\begin{itemize}
					\item \hard
					\item \easy
				\end{itemize}
				\item Video duration
				\begin{itemize}
					\item \longvideo
					\item \shortvideo
				\end{itemize}
				\item Video Count: \many
			\end{itemize}
		
			\para{Each course will have a subsection names as \say{Timing and Scheduling}. In this subsection I will talk about the difficulty of the course and how I will watch that course starting from summer and afterwards.}
		\end{sansserif}
		
		\clearpage		
		\section{Deep learning}
		\label{sec:courses:dl}
		\epigraph{
			\begin{sansserif}
				The career I chose: \textit{Data Science}, \say{The sexiest job of the 21st century,} \say{The best job in America,} \say{One of the newest and coolest jobs in IT world}
			\end{sansserif}
		}
		
		\begin{inparadesc}
			\item \hard
			\item \longvideo
		\end{inparadesc}
		\vspace{3mm}
		
		\para{Well as the quote says, this is exciting, BUT it really needs knowledge and effort to gain, the starting point is here: this nice deep learning course at \url{https://course.fast.ai/}.}
		
		\noindent\textbf{Practical Deep Learning}
		
		A free course designed for people with some coding experience, who want to learn how to apply deep learning and machine learning to practical problems.
		
		This free course is designed for people (and bunnies!) with some coding experience who want to learn how to apply deep learning and machine learning to practical problems.\newline
		
		\noindent Practical Deep Learning for Coders 2022 part 1, recorded at the University of Queensland, covers topics such as how to:
		\begin{itemize}
			\item Build and train deep learning models for computer vision, natural language processing, tabular analysis, and collaborative filtering problems
			\item Create random forests and regression models
			\item Deploy models
			\item Use PyTorch, the world’s fastest growing deep learning software, plus popular libraries like fastai and Hugging Face
		\end{itemize}
		
		\para{There are 9 lessons, and each lesson is around 90 minutes long. The course is based on our 5-star rated book\footnote{\url{https://www.amazon.com/Deep-Learning-Coders-fastai-PyTorch/dp/1492045527}}, which is freely available online\footnote{\url{https://course.fast.ai/Resources/book.html}}.}
		
		\para{You don’t need any special hardware or software—we’ll show you how to use free resources for both building and deploying models. You don’t need any university math either—we’ll teach you the calculus and linear algebra you need during the course.}
		
		\noindent\textbf{Your teacher}
		
		I am Jeremy Howard, your guide on this journey. I lead the development of fastai, the software that you’ll be using throughout this course. I have been using and teaching machine learning for around 30 years. I was the top-ranked competitor globally in machine learning competitions on Kaggle (the world’s largest machine learning community) two years running. Following this success, I became the President and Chief Scientist of Kaggle. Since first using neural networks 25 years ago, I have led many companies and projects that have machine learning at their core, including founding the first company to focus on deep learning and medicine, Enlitic (chosen by MIT Tech Review as one of the “world’s smartest companies”).
		
		I am the co-founder, along with Dr. Rachel Thomas, of fast.ai, the organization behind this course. At fast.ai we care a lot about teaching. In this course, I start by showing how to use a complete, working, very usable, state-of-the-art deep learning network to solve real-world problems, using simple, expressive tools. And then we gradually dig deeper and deeper into understanding how those tools are made, and how the tools that make those tools are made, and so on… We always teach through examples. We ensure that there is a context and a purpose that you can understand intuitively, rather than starting with algebraic symbol manipulation.
		
		\clearpage
		\para{Each lesson of the course has a video and a dedicated page of the website, like Lesson 1\footnote{\url{https://course.fast.ai/Lessons/lesson1.html}}}
		
		\noindent Notes:
		\begin{itemize}
			\item Each video is pretty long, on average they last one hour and 30 minutes! The longer the video, the more knowledge they contain AND the more attention they need AND the more practice as well.
			
			\item Each lesson has a \textit{How to complete lesson N} section (like this\footnote{\url{https://course.fast.ai/Lessons/lesson1.html\#how-to-complete-lesson-1}},) in which says: \textit{As well as watching the video and working through the notebooks, you should also read the relevent chapter(s) of the fast.ai book, Practical Deep Learning for Coders. Each lesson will tell you what chapter you need to read, just below the video}
		\end{itemize}
		
			\subsection{Timing and Scheduling}
				\para{This is a huge and difficult course, I must confess. However the instructor says: \say{We will teach you DL in a top-down approach AND will teach the same thing in different ways so that you will grasp the thing much more better and easier.}}
				
				\para{This is a 15-hour course. This is literally a long course specially when it has just 9 lessons. It depends a lot on the lesson, but the general timing and scheduling for this course will be as follows: Each lesson should be watched at \underline{one day}. It means that one lesson should not be watched at two days. The dedicated chapters of the book should be read according the explanations of the course website. One session may take one day for the video and one day for the book and one may take two or three says for the book, all I wanna say is that \underline{it will not be a fixed schedule} however it should be continuous. \textbf{It must not be interrupt or be cut.}}
				
		\clearpage
		\section{FastAPI}
		\epigraph{
			\begin{sansserif}
				\say{FastAPI framework, high performance, easy to learn, fast to code, ready for production}
			\end{sansserif}	
		}{\url{fastapi.tiangolo.com}}
		
		\begin{inparadesc}
			\item \easy
			\item \shortvideo
			\item \many
		\end{inparadesc}
		\vspace{3mm}
		
		\para{We all know FastAPI and there is no need for more introduction.
			The course I wanna watch is \url{https://youtu.be/0sOvCWFmrtA}}
		
		\noindent The course is a 19-hour long video which is downloaded and cut already. The important things are:
		\begin{itemize}
			\item The course is created one year ago and it is slightly outdated, so the documentation\footnote{\url{https://fastapi.tiangolo.com}} must be read along the course.
			
			\item Course will just show you how to use FastAPI and the real learning happens when doing projects.
			
			\item It's good to define nice projects whenever I came to an idea
			e.g. \textit{The API to send pictures of \url{https://unsplash.com} to my friends} :)
		\end{itemize}
			\subsection{Timing and Scheduling}
				\para{This is a course which is pretty long: about 19 hours of content, but it has a noticeable difference with the DL course: it has nearly 150 lessons and the durations of the lessons is short. Also FastAPI is easy, it is so so so much easier that DL. Besides all of this I wanna learn FastAPI fast and through the course away and do small to medium size projects with it. With all this considerations the timing and scheduling of this course will be as follows: I will watch and learn by concept. For example in \underline{week} or \underline{two or three days} I would learn the CRUD\footnote{Create, Read, Update and Delete; It is said to point the basic operations of a web API and database} operations of FastAPI.}
				
				\para{Doing projects with FastAPI is one of the critical and important things which I have to dedicate my time to do. Ideas for projects are much and will come to mind easily but doing them takes time and effort. After all \textbf{I should do projects.}}
				
				\para{I am learning FastAPI because back-end has very nice opportunity to get a job as a junior developer, also in MLOps\footnote{A career which is a mixture of Machine Learning + Development + Operations. It's all about data science but in a more DevOps manner.} I have to know back-end and Ops stuff well ({\small that's why I wanna learn docker as well.})} 
		
		\clearpage
		\section{From Deep Learning Foundations to Stable Diffusion}
		\epigraph{
			\begin{sansserif}
				\say{The beautiful world of AI, image and text manipulation and generation}
			\end{sansserif}	
		}{Me}
	
		\begin{inparadesc}
			\item \hard
			\item \longvideo
		\end{inparadesc}
		\vspace{3mm}
		
		\para{The course website: \url{https://course.fast.ai/Lessons/part2.html}}
		
		\para{Three years ago we pioneered Deep Learning from the Foundations, an in depth course that started right from the foundations—implementing and GPU-optimising matrix multiplications and initialisations—and covered from scratch implementations of all the key applications of the fastai library.}
		
		\para{This year, we’re going \say{from the foundations} again, but this time we’re going further. \textbf{Much} further! This time, we’re going all the way through to implementing the astounding Stable Diffusion\footnote{\url{https://stability.ai/blog/stable-diffusion-public-release}} algorithm. That’s the killer app\footnote{\url{https://www.pcworld.com/article/916785/creating-ai-art-local-pc-stable-diffusion.html}} that made the internet freak out\footnote{\url{https://devops.com/stable-diffusion-public-richixbw/}}, and caused the media to say\footnote{\url{https://arstechnica.com/information-technology/2022/09/with-stable-diffusion-you-may-never-believe-what-you-see-online-again/}} \say{you may never believe what you see online again}.}
		
		\para{Stable diffusion, and diffusion methods in general, are a great learning goal for many reasons. For one thing, of course, you can create amazing stuff with these algorithms! To really take the technique to the next level, and create things that no-one has seen before, you need to really deeply understand what’s happening under the hood. With this understanding, you can craft your own loss functions, initialization methods, multi-model mixups, and more, to create totally new applications that have never been seen before.}
		
		\para{Just as important: it’s a great learning goal because nearly every key technique in modern deep learning comes together in these methods. Contrastive learning, transformer models, auto-encoders, CLIP embeddings, latent variables, u-nets, resnets, and much more are involved in creating a single image.}
		
		\para{This is all cutting-edge stuff, so to ensure we bring the latest techniques to you, we’re teaming up with the folks that brought stable diffusion to the world: \url{stability.ai}. stability.ai are, in many ways, kindred spirits to fast.ai. They are, like us, a self-funded research lab. And like us, their focus is smashing down any gates that make cutting edge AI less accessible. So it makes sense for us to team up on this audacious goal of teaching stable diffusion from the foundations.}
		
		\para{The course will be available for free online from early 2023. But if you want to join the course right as it’s made, along with hundreds of the world’s leading deep learning practitioners, then you can register to join the virtual live course\footnote{\url{https://itee.uq.edu.au/event/2022/practical-deep-learning-coders-uq-fastai-part-2}} through our official academic partner, the University of Queensland (UQ). UQ will have registrations open in the next few days, so keep an eye on the link above.}
		
		\para{During the live course, we’ll be learning to read and implement the latest papers, with lots of opportunity to practice and get feedback. Many past participants in fast.ai’s live courses have described it as a “life changing” experience… and it’s our sincere hope that this course will be our best ever.}
		
		\para{To get the most out of this course, you should be a reasonably confident deep learning practitioner. If you’ve finished fast.ai’s Practical Deep Learning course\footnote{\url{https://course.fast.ai/}} then you’ll be ready! If you haven’t done that course, but are comfortable with building an SGD training loop from scratch in Python, being competitive in Kaggle competitions, using modern NLP and computer vision algorithms for practical problems, and working with PyTorch and fastai, then you will be ready to start the course. (If you’re not sure, then I strongly recommend getting starting with Practical Deep Learning now—if you push, you’ll be done before the new course starts!)}
		
		\para{If you’re an alumnus of Deep Learning for Coders, you’ll know that course sets you up to be an effective deep learning practitioner. This new course will take you to the next level, creating novel applications that bring multiple techniques together, and understanding and implementing research papers. Alumni of previous versions of fast.ai’s “part 2” courses have even gone on to publish deep learning papers in top conferences and journals, and have joined highly regarded research labs and startups.}
		
			\subsection{Timing and Scheduling}
				\para{I wrote the information of the course to just remember it. It won't be watched soon.}