\chapter{Habits}
	\begin{sansserif}
		\para{To continue to live and rest I found some ways to spend my leisure time, just like the books they've got small tags to make them more clear.}
		
		\noindent The tags:
		\begin{enumerate}
			\item \always which says this item has no specific time.
			\item \weekend the weekends are good for this item
			\item \timetotime you can do it whenever you want to
			\item \normal needs body activity
			\item \rest	is done to rest and NOT to think about anything else
		\end{enumerate}
	\end{sansserif}

		\section{Podcast}
			\epigraph{
				\begin{sansserif}
					 \say{Listening to podcast, reading a book, listening to an audiobook and watching films isn’t waste of time. It’s how somebody becomes wise!}
				\end{sansserif}	
			}{Deyth Banger}
		
			\begin{inparadesc}
				\item \timetotime
				\item \normal
			\end{inparadesc}
			\vspace{2mm}
			
			\para{Talk Python to Me is a weekly podcast hosted by developer and entrepreneur Michael Kennedy. We dive deep into the popular packages and software developers, data scientists, and incredible hobbyists doing amazing things with Python. If you're new to Python, you'll quickly learn the ins and outs of the community by hearing from the leaders. And if you've been Pythoning for years, you'll learn about your favorite packages and the hot new ones coming out of open source.}
						
			\para{Listening to old and new Python podcasts, specially from \textit{Talk Python to Me} channel helps a lot, It provides many information, introduces mane new technologies and brings many good people to the show.}
			
		\section{Music}
			\epigraph{
				\begin{sansserif}
					\say{Music doesn't lie. If there is something to be changed in this world, then it can only happen through music.}
				\end{sansserif}
		    }{Jimi Hendrix}

			\begin{inparadesc}
				\item \always
			\end{inparadesc}
			\vspace{2mm}
		
			\para{As always: \textit{I live because of my musics} :)}
			
		\section{Films}
			\epigraph{
				\begin{sansserif}
					\say{Movies are like an expensive form of therapy for me.
				\end{sansserif}
			}}{Tim Burton}
		
			\begin{inparadesc}
				\item \weekend
				\item \rest
			\end{inparadesc}
			\vspace{2mm}
			
			\para{Watching new films and series, enjoys a LOT. The dedicated series which I want to watch is \textit{The Mentalist}. A TV show which remembers me of Sherlock!}
			
			\para{Also I will download the films which I haven't watch in 1080p quality and enjoy the leisure :)}
			
		\section{Biking}
			\epigraph{
				\begin{sansserif}
					\say{Life is like riding a bicycle. To keep your balance you must keep moving}
				\end{sansserif}	
			}{Albert Einstein}
			
			\begin{inparadesc}
				\item \timetotime
				\item \normal
			\end{inparadesc}
			\vspace{2mm}

			\para{Physical activity to become fresh again, and to empty the mind outta the learned stuff is really important and Biking has to be done in summer.}
	

