\chapter{\textsf{Preface}}	
		\para{After going up and down in my life, I finally found the way to study and learn well. This document has everything I want to do and resource I want to check. This plan will be started from the summer of 1402 (2023.)}
			
		\para{After spending one whole semester in the university\footnote{the 3rd semester}, it is got clear to me, that \underline{meanwhile} studying, learning \textbf{new}  things, is hard! It's possible but it's hard. So summers are the times which I have to value a lot and to make the most outta 'em.}
		
		\para{At the time of writing this, there are 5 days remaining of the year, a long and hard year both for Iran, my love, and myself. I learned and grew a lot during this year. I spend a whole semester in university, experienced a really \textit{Randomly-Generated-but-Related} journey. Studied a lot, learned how to study well and meet many new and nice people.}
		
		
		\para{But after all, I have to create a path to my actual career! This is the most important thing which I have to take care of. After working, searching and talking to many people, I've finally made my decision and chosen: \textit{Data Science}. I really like this field, it's very amazing but hard to learn :) Beside this, I wanna learn backend engineering as well, 'cause it is much faster (faster to get result, lol) and has a slightly smaller learning curve.}
		
		\para{This plan will be started from the summer of 1402 (2023), but I will be working and adding things to this document from time to time; there may be some new chapters or reorganization of the chapter but not now \textsf{:D}}
		
		\para{This will be a hot summer. It gets hot because of so many hours I want to study, both with video courses and with reading books. To learn data science I asked someone in our university who already is a data scientist, and he introduced me to the deep learning course of \textit{Jeremy Howard}. This course is freely available on YouTube. Also this course needs a book nearby (written by Jeremy Howard) called \textit{Deep Learning for Coders With Fastai and PyTorch}.}
		
		\para{Besides learning data science, learning new things and refreshing my Python skills is something that I would never miss and enjoy a lot. The focus of this summer will be on the CPython implementation itself, so I've chosen some nice books on this field. I have gathered some more general books on Python too, but they would have a lesser priority.}
		
		\para{Watching video courses and reading books are the main activities of the summer, but without spending or more precisely, \textit{acquiring} time to rest, nobody can learn anything; listening to music and podcast and watching movies are the main non-active and biking is the main physical activity of my summer.}

